Efficient, Robust and Exact Boolean Operations on N Triangular Mesh Primitives

### 2016-08-08 summary.tex
0808

\usepackage{enumitem}
%\usepackage[]{algorithm2e}
\usepackage[]{algpseudocode}
\usepackage{algorithm}
\usepackage{multirow}
\usepackage{slashbox}
\usepackage{color}
%\usepackage{ulem}
%\usepackage[numbers,sort&compress]{natbib}
\renewcommand{\arraystretch}{1.3}

@@

\IEEEtitleabstractindextext{
\begin{abstract}
  Constructive solid geometry is widely used for computer aided design and manufacturing. However, boolean operations, which compute the boundary representation of constructive solid geometry, has been suffered from robustness and efficiency problem for more than three decades. In this paper, we propose a fast and exact boolean operation approach which is theoretically robust for valid triangle mesh inputs. This is done by introducing plane-based geometry into boolean operations and strictly follow the principle of no constructions during processing. Different from previous BSP-based method, our method works on halfedge, with only one-time conversion to the plane representation in intersection areas, instead of a series of complex conversions between different representations. Also, by using geometry connectivity and space neighboring information, our method reuse the computation iteratively, saving much computation time. Comparison experiments with state-of-the-art techniques show that our method is unconditionally exact and robust, while is competitively efficient with non-robust methods and much faster than exact, robust ones.
\end{abstract}

@@

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
\IEEEPARstart{C}{onstructive} solid geometry (CSG) has long been a popular modeling tool of computer-aided design and computer-aided manufacturing (CAD/CAM). It constructs complex models by combining primitives using a series of regularized Boolean operations \cite{requicha1977mathematical,tilove1980closure}: union, intersection and difference. CSG can be converted into the widely-used boundary representation (i.e., triangle mesh) through boolean operations, which is an classical topic with history of over three decades.

In general, there are two major types of Boolean algorithms according to how they deal with intersection between primitive meshes. Approximate methods redicretize the intersection areas, fit vertices approximatively and rearrange topology. On the other hand, exact method do not change vertex positions, retain as many input elements as possible (e.g., faces, vertices and topology). In many applications, exact methods are preferred for there accuracy. Also, using exact methods, the clear mapping between the surface of input and output meshes makes it easier for the inheritance of information like face colors and materials. However, for exact boolean operation methods, there is always a bargain between robustness and efficiency. Recent exact boolean operation methods try to find a faster way to compute boundaries of CSG. However, for robustness, the answers are often exact arithmetic \cite{barki2015exact,zhou2016mesh} or trivial workarounds, like setting a tolerance \cite{feito2013fast,segal1990using} or rotating the primitive with small angles to avoid coplanar cases \cite{douze2015quickcsg}. However, none of the solution is good enough. While exact-arithmetic based methods are significantly slower, workarounds are often case dependent and not reliable for complex CSGs.

We develop an unconditionally robust and exact boolean operation method for triangle meshes without using exact arithmetic. The robustness of our method is based on the observations by Sugihara and Iri \cite{sugihara1990solid} that boolean operations can be performed requiring geometry constructions if representations are based on planes and not vertices. This idea of using plane-based representation has been developed by Berstein and Fussell \cite{bernstein2009fast} by combining it with binary search partition (BSP) techniques \cite{naylor1990merging,thibault1987set}. Later, Campen et. al. \cite{campen2010exact} improved the method using octrees to resolve intersections locally, avoiding inefficient large BSP tree construction. Despite of that, Campen et. al.'s method still suffers from performance problem because of the complex conversions among B-reps, plane-based representations and BSP representations. Also, the incoherence between BSP representation, where boolean operations actually happens, and B-reps, which are input and output meshes, requires an extra stitching step to connect the reconstructed intersection areas with the untouched
meshes, leading to extra computation burden.

We adopt plane-based techniques and strictly follow the principle of no geometry construction, yet develop a very different framework based on halfedges, requiring only one-time conversion to the plane representation in intersection areas. Since the geometry connectivity is stored in halfedge, it allow us to take advantage of geometry connectivity for classification acceleration \cite{feito2013fast,ogayar2015deferred,updegrove2016boolean}, which is hard to for a BSP-based method. In addition, our method can perform boolean operations with more than two primitives in one call, instead of recursively doing binary boolean operations. In this way, extra complexity of our method is introduced. But we can save much computation time by avoiding repetitive computation. The experiment shows that our method is much faster than Campen et. al.'s method, while only about two to three times slower than the state-of-art non-robust method \cite{douze2015quickcsg}.

@@

\subsection{Exact methods}

Boolean operations have long been notorious with robustness issue since its inception in the 1980s \cite{requicha1985boolean, laidlaw1986constructive}. Many researchers have attempted to solve such an issue using arbitrary precision arithmetic \cite{banerjee1996topologically, fortune1995polyhedral, keyser2004esolid, granados2003boolean, hachenberger2005boolean} and exact interval computation \cite{fang1993robustness, hu1996robust, segal1990using}. However, these methods are often too expensive in computation time and memory to be practical for evaluation of CSG with massive faces. For example, in the Computational Geometry Algorithms Library (CGAL) \cite{cgal:hk-bonp3-15a}, the state-of-the-art robust Boolean operation algorithm \cite{hachenberger2005boolean} (implemented with arbitrary precision arithmetic) is more than 20 times slower than its non-robust version.

\subsection{Approximative methods}

With the development of general-purpose computing on graphics processing units (GPGPUs), many researchers  \cite{wang2011approximate, zhao2011parallel, museth2002level, chen1999volumetic, eisemann2008single} have tried to utilize the grand computation power of graphics hardware for Boolean operations. These methods often have good performance and are suitable for interactive applications, such as digital sculpting. However, owing to the paralleled features of graphics hardware, these methods are usually voxel-based and support only approximate evaluation that inevitably suffers from geometric detail loss, especially at the intersection areas of primitives.

\subsection{Plane-based geometry representation}

The primary information of commonly used representation of solids are the vertex coordinates. In this way, edges and faces are implicitly represented by combination of vertices. In contrast, in plane-based representation, the primary elements are planes. Vertices and edges are all implicitly represented by plane intersections.

The concept of plane-based representation of polygonal meshes was first described by Sugihara and Iri \cite{sugihara1990solid}. Plane-based representation provides one important advantage
when it comes to tasks that involve changing the topology of solids represented by meshes like the evaluation of Boolean expressions: no new primary geometry information has to be constructed to obtain the resulting polyhedron ¨C it is composed of a subset of the planes of the input polyhedra. Hence, opposed to the case of using vertex coordinates, that inevitably necessitates the construction of new geometry information, only geometric decision predicates are required to compose the output polyhedron from the face planes of the input. Since the input is usually given in a numerical representation with finite precision, we can determine an upper bound on the precision that is needed to make correct decisions. The a priori knowledge of this upper bound allows us to use fixed precision predicates that are specifically tailored to the precision required in the worst case, resulting in a vastly better performance compared to techniques for arbitrary numerical precision, that are usually required when
constructions are part of the processing. Our processing is rigorously based on this paradigm of plane-based geometry representation that allows us to perform fully robust, exact computations using only fast fixed precision predicates. These predicates take planes as arguments and check coincidence and co-orientation of planes, orientation of a plane with respect to a point defined by the intersection of three planes, and whether three planes intersect in a unique point. The latter one can also be used in negated form to check if three planes, that are known to intersect in a common point, even intersect in a common line. We implement them using filtering techniques proposed by Shewchuk.

@@

\label{sec:overview}
Our method is designed for boundary evaluation of Boolean operations on arbitrary number of primitives. Input primitives should be watertight and non-manifold  triangle meshes, represented by halfedge structures\cite{mcguire2000half}. Our method is unconditional robust, exact, while keeping good performance. In this section, we first introduce the motivation of our method, then describe where we start to design our boundary evaluation method. At last, we give the overview of the method.

\subsection{Motivation}
\label{sec:paradigm}

The boundary evaluation is in essence a process of selection. In other words, given a Boolean function, it reserves those primitive faces that pass the function and drop the others to generate the final mesh. Unfortunately, for B-reps primitives such as triangle mesh, not all the facets from the input primitives can be classified in a whole, since some of them intersect other primitives. Therefore, we need an extra step aiming at detecting the intersection between primitives and performing the tessellation. In general, most of the boundary evaluation methods follow the two-step paradigm  \cite{wang2011approximate} above, which consists of intersection computation and face classification.

During the intersection computation, primitive facets are tested in pairs to compute their intersection. Each input primitives are tessellated according to the intersection test results, making every face be either inside, outside or on the boundary of other primitives. They are what we called \emph{non-intersected meshes}. Every face of non-intersected meshes can be classified in a whole during classification. Unfortunately, under common float-point coordinate system, intersection test is error-prone. There are mainly two causes: first, there are a large amount of degenerate cases which are hard to be exactly detected; second, when there are intersections, new vertices are introduced into the geometry, whose coordinates usually can not be exactly represented by float-point number.

Face classification is to evaluate whether a given face $x$ belongs to the final geometry according to the n-primitive Boolean function $f$ :
\begin{equation}
\lambda_f(x) = f(\boldsymbol{\Lambda}(x)) = f(\lambda_1(x), \lambda_2(x), \cdots, \lambda_n(x)).
\end{equation}
The parameter $\lambda_i(x)$ is space indicator with respect to primitive $P_i$. This means to classify a face, one has to know the space indicators with respect to all the primitives (or the whole indicator vector $\boldsymbol{\Lambda}(x)$ for short). A space indicator has four conditions: completely inside (\emph{in}), completely outside (\emph{out}), on the boundary with consistent normals (\emph{same}) or opposite normals (\emph{oppo}). The rules of Boolean function evaluation by these indicators are described in \cite{douze2015quickcsg}\cite{feito2013fast}.

Face classification also suffers from robustness and exactness problems. Many methods classify face according to the indicators of its barycenter, and use point-in-polyhedron test to compute these indicators. However, coordinates of barycenters cannot be exactly represented and have the potential to generate false classification. In addition, to classify a single face, all the components of its space indicator vector must be figured out. Considering the large amount of faces, acceleration is usually necessary. Many algorithms take the benefits of the local coherence of indicators, classifying neighboring faces together. While this does improve the performance, it can make the exactness problem worse because the false classification can be propagated to neighboring faces.

We want to develop a new boundary evaluation method based on the two-step paradigm, keeping unconditional robust, exact and as fast as possible. Combined with the analysis above, we think our method should includes the following features:
\begin{itemize}
    \item It has to avoid errors when introducing new vertices during intersection computation. All degenerate cases of intersection have to be well resolved.
    \item Face classification has to be exact. On the other hand, acceleration using local coherence of indicators may be helpful.
    \item The exactness and robustness should not rely on arbitrary precision arithmetic, because it is too slow. Instead, we choose the plane-based techniques from \cite{bernstein2009fast}\cite{campen2010exact} to ensure good performance.
\end{itemize}

\subsection{Linked halfedge}

\label{sec:meshes}
We make an essential observation that the non-intersected meshes, as intermediate result of intersection computation, plays a very important role of the method design. It is a bridge that controls the complexity of intersection computation and facilitates the face classification. After the non-intersected meshes is determined, all things left are how to construct such a data structure and how to classify according to it.

Our non-intersected mesh, called Linked Halfedge, is a variance of halfedge, a well-known data structure to represent solids. Halfedge has two advantages: first, since halfedge is popular, using it as the intermediate data structure can avoid unnecessary conversion, which has the potential to create simpler algorithm and better performance and result topology; second, the geometry connectivity, by which we accelerate classification using local coherence of space indicators, can be easily retrieved through halfedge.

However, naive halfedge is far from enough. The vertex coordinates in halfedge are usually represented by float point number, which cannot exactly represent the newly introduced intersection points. Therefore, we utilize plane-based representation to avoid computing new coordinates. In addition, we detect all coincident vertices among primitives and linked them together (that is why it is called Linked Halfedge). This information is used for avoiding repetitive vertices, reconstructing geometry connectivity, and ensuring the topology correctness.

Enlightened by Feito et. al. \cite{feito2013fast}, we found that the the topology near intersection lines between faces can benefit point-in-polyhedron test by dramatically reducing the number of faces needing traversing. Therefore, we add extra information into the Linked Halfedge, called \emph{intersection context}, to facilitate afterwards face classification. Intersection context identifies where an intersection lies on the surface of the related primitives. An edge of Linked Halfedge has intersection context only if it is coincident with a certain intersection line segment between primitives. We will give the definition and usage of intersection context in details in the following sections.

To give a overall impression of how we design Linked Halfedge, we summarize the above content and highlight the following features:

\begin{itemize}
  \item Each input primitive mesh is tessellated into a Linked Halfedge. Faces in a Linked Halfedge must not cross any other Linked Halfedges.
  \item Coincident vertices between different Linked Halfedge should be linked, that is, coincident vertices are shared among Linked Halfedges.
  \item If a certain edge of Linked Halfedge is coincident with intersection line segment(s), it should be associated with the corresponding intersection context(s).
\end{itemize}

\subsection{Method overview}

@@

This step is the preparation of intersection detection. As intersection detection is performed between each pair of faces, localization is necessary to filter invalid pairs beforehand. In general, any space division data structure can be applied in this step. We use the adaptive octree for its simplicity. Our implementation is akin to the implementation in \cite{ogayar2015deferred}. Intersection between triangle faces and octree leaves can be efficiently detected using the separating axis theorem \cite{gottschalk1996obbtree}. Octree leaves are classified into two types: if all faces that intersect a leaf belong to the same primitive, we call it a \emph{non-critical cell}. Otherwise, it is a \emph{critical cell}.

The difference between our space division and many others \cite{ogayar2015deferred}\cite{feito2013fast} is the octree node subdivision termination criterion. In our method, we do not need subdivide any non-critical cell no matter how many faces it contains. This is because subdividing non-critical cells benefits only the ray-casting point-in-polyhedron test, which rarely appears in our method. This simplification can bring large performance advantage, especially for those cases where intersections between primitives are not complex and limited in small regions.

@@

This step is to detect intersections between primitives in a robust and exact way. Our algorithm is largely based on vertex-based M\"{o}ller's algorithm \cite{moller1997fast}, which is very efficient to compute intersection between two triangles. However, naive implementation of M\"{o}ller's algorithm always incurs robustness issues when computing the coordinates of new vertices. To avoid an unexpected failure caused by numeric errors, we integrate plane-based representation of polyhedra \cite{sugihara1990solid} into the implementation of M\"{o}ller's algorithm. Adaptive precision predicate technique \cite{shewchuk1997adaptive} is applied for efficiency of plane-based geometry computation. Moreover, to make our method robust, we classify all the intersection cases into three major classes and respectively discuss how to each condition. Details are provided in Section \ref{section:isect}.

@@

Once all intersections are detected, we need to tessellate the input primitives and construct the Linked Halfedges.. In many methods like \cite{ogayar2015deferred}, constraint Delaunay triangulation (CDT) is applied to perform tessellation, since the intersections are naturally the constraints of CDT. However, for a CSG with more than two primitives, the intersection vertices may be generated by intersections of three faces from different primitives, which cannot be computed during the previous step. Also, intersection line segments may overlap or intersect with each other, and cannot be used for constraints of CDT directly. Finally, as our intersection vertices are represented exactly by planes, implementation of CDT could be complex and inefficient, as most CDT methods were not designed to handle planes. Therefore, we design a simple structure, called Tess-graph, to guide the tessellation of each single face, and develop a very fast but exact method to construct Linked Halfedges from Tess-graphs, which is suitable for dealing with plane-based representation of intersections. Details are shown in section \ref{sec:tessellation}.

@@

This step is to choose faces from the Linked Halfedges to generate the final mesh. Literally compute all the space indicators of each face is unacceptable slow for large CSG trees. Enlightened by Feito et. al. \cite{feito2013fast}, we utilize the geometry connectivity to accelerate this process. In Feito et. al.'s method, the faces of tessellated meshes are first grouped according to whether they have the same indicator vector. After the grouping, each group is classified as a whole. This is based on the observation that indicators of faces are spatially coherent. That is, if a face $f$ is outside of primitive $M_0$, the neighbor of $f$ are likely to be out of $M_0$, too. Different from Feito et. al.'s method, we also consider the condition when the number of primitives is larger than two. In this condition, space vector of a face may be partly the same with its neighborhoods'. That is, we allow space indicators not only share within faces of the same group, but also among different groups and even primitives. This is useful when the number of primitives is large, or intersections between primitives is complex. Details will be shown in section \ref{sec:classification}.

@@

Vertex coordinates are commonly used in geometry computation. However, vertex coordinates suffer from inexact representation of intersection point between primitives. Therefore, we choose to use planes-based representation of polyhedrons and implicitly represent vertex by plane intersection. We start with a quick review of the basic conception of plane-based representation. After that, we introduce two substrates related to plane-based representation used in our method, since these two are rarely seen in related researches. Other substrates of plane-based representation can be seen in \cite{bernstein2009fast}.

>>>>

\usepackage{enumitem}
%\usepackage[]{algorithm2e}
\usepackage[]{algpseudocode}
\usepackage{algorithm}
\usepackage{multirow}
\usepackage{slashbox}
\usepackage{color}
\usepackage[numbers,sort&compress]{natbib}
%\usepackage{ulem}
%\usepackage[numbers,sort&compress]{natbib}
\renewcommand{\arraystretch}{1.3}

@@

\IEEEtitleabstractindextext{
\begin{abstract}
  Constructive solid geometry is widely used for computer aided design and manufacturing. However, boolean operations, which compute the boundary representation of constructive solid geometry, have been suffered from robustness and efficiency problem for more than three decades. In this paper, we propose a fast and exact boolean operation approach which is theoretically robust for valid triangle mesh inputs. This is done by introducing plane-based geometry into boolean operations and strictly follow the principle of no constructions during processing. Different from previous BSP-based method, our method works on halfedge, with only one-time conversion to the plane representation in intersection areas, instead of a series of complex conversions between different representations. Also, by using geometry connectivity and space neighboring information, our method reuse the computation iteratively, saving much computation time. Comparison experiments with state-of-the-art techniques show that our method is unconditionally exact and robust, while is competitively efficient with non-robust methods and much faster than exact, robust ones.
\end{abstract}

@@

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
\IEEEPARstart{C}{onstructive} solid geometry (CSG) has long been a popular modeling tool of computer-aided design and computer-aided manufacturing (CAD/CAM). It constructs complex models by combining primitives using a series of regularized boolean operations \cite{requicha1977mathematical,tilove1980closure}: union, intersection and difference. CSG can be converted into the widely-used boundary representation (B-rep) through boolean operations, which is an classical topic with history of over three decades.

In general, there are two major types of boolean algorithms according to how they deal with intersection between primitive meshes. Approximate methods redicretize the intersection areas, fit vertices approximatively and rearrange topology. On the other hand, exact method do not change vertex positions, retain as many input elements  (e.g., faces, vertices and topology) as possible. In many applications, exact methods are preferred for their accuracy. Also, using exact methods, the clear mapping between the surface of input and output meshes makes it easier for the inheritance of information like face colors and materials. However, for exact boolean operation methods, there is always a bargain between robustness and efficiency. Recent exact boolean operation methods try to find faster ways to compute boundaries of CSG. However, for robustness, the answers are often exact arithmetic \cite{barki2015exact,zhou2016mesh} or trivial workarounds, like setting a tolerance \cite{feito2013fast,segal1990using} or rotating the primitive with small angles to avoid coplanar cases \cite{douze2015quickcsg}. However, none of the solution is good enough. While exact-arithmetic based methods are significantly slower, workarounds are often case dependent and not reliable for complex CSGs.

We develop an unconditionally robust and exact boolean operation method for triangle meshes without using exact arithmetic. The robustness of our method is based on the observations by Sugihara and Iri \cite{sugihara1990solid} that boolean operations can be performed requiring geometry constructions if representations are based on planes and not vertices. This idea of using plane-based representation has been developed by Berstein and Fussell \cite{bernstein2009fast} by combining it with binary search partition (BSP) techniques \cite{naylor1990merging,thibault1987set}. Later, Campen et. al. \cite{campen2010exact} improved the method using octrees to resolve intersections locally, avoiding inefficient large BSP tree construction. Despite of that, Campen et. al.'s method still suffers from performance problem because of the complex conversions among B-reps, plane-based representations and BSP representations. Also, the incoherence between BSP representation, where boolean operations actually happens, and B-reps, which are input and output meshes, requires extra steps to connect the reconstructed intersection areas with the untouched meshes, leading to extra computation burden and complex topology.

We adopt plane-based techniques and strictly follow the principle of no geometry construction, yet develop a very different framework based on halfedges, requiring only one-time conversion to the plane representation in intersection areas. Since the geometry connectivity is stored in halfedge, it allow us to take advantage of geometry connectivity for classification acceleration \cite{feito2013fast,ogayar2015deferred,updegrove2016boolean}, which is hard to for a BSP-based method. In addition, our method can perform boolean operations with more than two primitives in one call, instead of recursively doing binary boolean operations. In this way, extra complexity is introduced. But we can save much computation time by avoiding repetitive computation. The major difficulty of applying plane-based representation on halfedge is by the incoherence between the two representations. Halfedge is a vertex-based representation. Many geometry operations (e.g., coordinates projection and compute the barycenter coordinate of triangle) available on halfedge can be very complex and thus inefficient under plane-based representation. On the other hand, we have to compute under plane-based representation for exactness and robustness. Therefore, we manage to limit our computation of boolean operations to several basic plane-based predicates. The experiment shows that our method is much faster than Campen et. al.'s method, while only about two to three times slower than the state-of-art non-robust method \cite{douze2015quickcsg}.

@@

Boolean operations have long been researched for over three decades since it inception in the 1980s \cite{requicha1985boolean, laidlaw1986constructive}. Most previous work of boolean operations can be classified into two categories: exact and approximate methods. Exact methods retain vertex positions. And the topology of the input meshes is also preserved as much as possible. The coordinates of intersection points between input meshes are computed by input configurations to construct the topology around intersection. However, the coordinates cannot be represented exactly using fix-precision float point numbers and the robustness is often a problem. Using exact arithmetic is too expensive in computing. Therefore, exact methods face the problem of the balance between performance and robustness. On the other hand, approximate methods rediscretize the input mesh surfaces using techniques such as voxels, octrees and Layered Depth Images and can reach better performance and robustness.

\subsection{Exact Methods}

\begin{figure}[t]
\centering
\includegraphics[width=2.5in]{coplanarexample}
\caption{{\color{red}{Sketch: the example of coplanar cases in a boolean operations with four cylinders}}}
\label{fig:coplanarexample}
\end{figure}

For exact methods, some \cite{ogayar2015deferred,douze2015quickcsg,zhou2016mesh,xu2013fast,feito2013fast} pursues efficiency but cannot guarantee robustness in degenerate cases such as coplanar conditions. Most of them are implemented by fix-precision float-point arithmetic and round errors accumulation is often inevitable. Douze et al. \cite{douze2015quickcsg} implemented very efficient boolean operations that can handle very large meshes. Also, their method is able to perform variadic boolean operations: evaluating the final result mesh of CSG all at once instead of decomposing the CSG into a series of binary boolean operations. However, their method cannot deal with coplanar cases nor guarantee accuracy for common situations. On the contrary, CSGs with large meshes contain are more complex and more likely to contain degenerate cases. Also, coplanar cases can regularly happens for man-made artifact modeling (Fig. \ref{fig:coplanarexample}) and should not be treated as exceptions for boolean operation methods.

Many researchers have attempted to solve robustness issue for exact boolean operations using arbitrary precision arithmetic \cite{banerjee1996topologically, fortune1995polyhedral, keyser2004esolid, granados2003boolean, hachenberger2005boolean} and exact interval computation \cite{fang1993robustness, hu1996robust, segal1990using}. These methods are often too expensive in computation time and memory to be practical for CSG with massive faces. For example,
the current standard of robust exact boolean operations method is CGAL's \cite{cgal:hk-bonp3-15a} exact-arithmetic implementation \cite{granados2003boolean} of Nef polyhedra \cite{bieri1988elementary}. It requires conversions between Nef polyhedra and input mesh data structures during evaluation and is more than 50 times slower than non-robust booleans \cite{bernstein2009fast}.

\subsection{Approximative Methods}

Since efficiency, accuracy and robustness seem unable to be obtained at the same time, starting from \cite{museth2002level}, some sacrifice accuracy for better efficiency and robustness. Most of such methods are based on conversion to volumetric representations. However, the quality of result mesh depends on the resolution of the volume grid and better quality requires higher resolution. To accelerate this process, some try to reduce the complexity of the output mesh \cite{varadhan2004topology} and others try to preserve non-intersected areas of the input mesh to avoid redundant tessellation \cite{pavic2010hybrid,wang2011approximate,zhao2011parallel,hable2005blister,ogayar2006gpu}. Also, with the development of general-purpose computing on graphics processing units, many of them utilize the grand computation power of graphics hardware for boolean operations. These methods often have good performance and are suitable for interactive applications. However, the fundamental problem of approximate methods is owing to grid-depend nature of volumetric calculations: they inevitably suffers from geometric detail loss and unwieldy topology changes.

\subsection{Plane-Based Methods}
\label{sec:pbrelated}

The concept of plane-based representation of polygonal meshes was first described by Sugihara and Iri \cite{sugihara1990solid}. Such representation provides important advantage that for boolean operations, no new primary geometry information has to be constructed to obtain the result polyhedron---it is composed of a subset of the planes of the input polyhedra. Berstein and Fussell \cite{bernstein2009fast} combined the plane-based representation with binary space partitioning (BSP) \cite{thibault1987set,naylor1990merging} to develop an unconditionally robust boolean operation method. Compared to volume-grid based methods, their BSP-based method increases mesh complexity more moderately and the input topology can be reconstructed better. However, it requires conversions between input data structures and plane-based representation which are inefficient from both storage and time views. Also, the merge of two BSP trees is an $O(mn)$ time complexity process, where $m$ and $n$ are the size of the trees. It makes this method impractical for very large input meshes. Campen and Kobbelt \cite{campen2010exact} improved their method by localization using an octree. And the refinement only takes place locally near intersections.

@@

\label{sec:overview}
Our method is designed for boolean operations on arbitrary number of triangle meshes. Input mesh primitives are required to be watertight and not self-intersected, with manifold surface, represented by wide-used halfedges \cite{mcguire2000half}. Despite of so many constraints, our method is not sensitive to topology deficiencies and works well if deficiencies are not near the intersection areas between meshes.

\subsection{Background \& Motiviation}
\label{sec:paradigm}

The boolean operation of triangle meshes is in essence a process of selection. In other words, given a boolean function, it reserves those primitive faces that pass the function and drop the others to generate the final mesh. Unfortunately, for B-reps primitives such as triangle mesh, not all the facets from the input primitives can be classified as a whole, since some of them intersect other primitives. Therefore, we need an extra step aiming at detecting the intersection between primitives and performing tessellation. Most of the boolean operation methods follow this two-step paradigm, which consists of intersection computation and face classification. So is our method.

During the intersection computation, primitive facets are tested in pairs to compute their intersections. Each input meshes are tessellated according to the intersection results, making every face be either inside, outside or on the boundary of other primitives. The retessellated meshes are what we called \emph{non-intersected meshes}. Unfortunately, under fix-precision float-point arithmetic, intersection test is error-prone for two causes: first, there are a large amount of degenerate cases which are hard to be precisely classified; second, when there are intersections, new vertices are introduced into the geometry, whose coordinates cannot be exactly represented by float-point numbers.

The second step, face classification, is to evaluate whether a given face $x$ belongs to the final geometry according to the n-primitive boolean function $f$ :
\begin{equation}
\lambda_f(x) = f(\boldsymbol{\Lambda}(x)) = f(\lambda_1(x), \lambda_2(x), \cdots, \lambda_n(x)).
\end{equation}
The parameter $\lambda_i(x)$ is space indicator with respect to primitive $P_i$. To classify a single face $x$, one has to know the space indicators with respect to all the primitives (or their vector representation $\boldsymbol{\Lambda}(x)$). A space indicator has four conditions: completely inside (\emph{in}), completely outside (\emph{out}), on the boundary with consistent normals (\emph{same}) or opposite normals (\emph{oppo}). The rules of Boolean function evaluation by these indicators are described in \cite{douze2015quickcsg,feito2013fast}.

\begin{figure}[t]
\centering
\includegraphics[width=2.5in]{falseclass}
\caption{{\color{red}{Sketch: False classification}}}
\label{fig:falseclass}
\end{figure}

Face classification also suffers from robustness and exactness problems. Many methods classify face according to the indicators of its barycenter, which can be computed by point-in-polyhedron test \cite{feito2013fast,campen2010exact}. However, coordinates of barycenters cannot be exactly represented and have the potential to generate false classification (Fig. \ref{fig:falseclass}). In addition, for the large amount of faces and input meshes, many methods take the benefits of the local coherence of indicators, classifying neighboring faces together \cite{pavic2010hybrid,feito2013fast,ogayar2015deferred,zhou2016mesh}. While this does improve the performance, it can make the robustness problem worse because the false classification may be propagated to neighboring faces.

We want to develop an exact boolean operation method based on the two-step paradigm, being unconditional robust and as fast as possible. Considering the analysis above, we think our method have to include the following features:
\begin{itemize}
    \item Intersection computation has to avoid errors when introducing new vertices into meshes.
    \item All degenerate cases of intersection between input meshes have to be well resolved.
    \item Face classification has to be exact and robust.
    \item Acceleration using geometry connectivity is necessary for face classification.
\end{itemize}

For efficiency, the exactness and robustness should not rely on arbitrary precision arithmetic. Instead, we choose the plane-based techniques from \cite{campen2010exact}. However, as we discussed in section \ref{sec:pbrelated}, BSP structure does not support geometry connectivity query in nature, and we do not want fussy conversions between different representations. Therefore, we use halfedge instead as our major data structure and embed plane-based representation into it.

\subsection{Linked Halfedge}

\begin{figure}[t]
\centering
\includegraphics[width=2.5in]{linkedhalfedge}
\caption{{\color{red}{Sketch: The Linked Halfedge structure}}}
\label{fig:linkedhalfedge}
\end{figure}

\begin{figure*}[!t]
\centering
\includegraphics[width=7.1in]{flowchart}
\caption{{\color{red}{Sketch: overview, will be replaced}}}
\label{fig:overview}
\end{figure*}

\label{sec:meshes}
We made an observation that the non-intersected meshes, as intermediate result of intersection computation, plays an important role of boolean operations. It is a bridge that controls the complexity of intersection computation and facilitates face classification. After the data structure of non-intersected meshes is determined, all things left are how to construct this structure and how to classify according to it.

Our non-intersected mesh, called Linked Halfedge (Fig. \ref{fig:linkedhalfedge}), is a variance of halfedge, a wide-used data structure to represent solids. Halfedge has two advantages: first, since halfedge is popular, using it as the intermediate data structure can avoid unnecessary conversion, which has the potential to have better performance and result topology; second, the geometry connectivity, by which we accelerate classification using local coherence of space indicators, can be easily retrieved through halfedge.

However, naive halfedge is far from enough. The vertex coordinates in halfedge are usually represented by float point number, which cannot exactly represent the newly introduced intersection points. Therefore, we utilize plane-based representation to avoid computing new coordinates. In addition, we detect all coincident vertices among input meshes (including intersection vertices). This information is used for avoiding repetitive vertices in the final mesh, reconstructing geometry connectivity, and ensuring the topology correctness.

Enlightened by Feito et. al. \cite{feito2013fast}, we found that the the topology near intersection lines between faces can benefit point-in-polyhedron test by dramatically reducing the number of faces needing traversing. Therefore, we add what we call \emph{intersection context} into the our non-intersected meshes to facilitate afterwards face classification. Intersection context identifies where an intersection lies on the surface of the related primitives. An edge of Linked Halfedge stores intersection context only if it is coincident with a certain intersection line segment between primitives. We will give the definition and usage of intersection context in details in section \ref{sec:ir}.

To give an overall impression of Linked Halfedge, we summarize the above content and highlight the features of Linked Halfedge as follows:

\begin{itemize}
  \item Each input mesh is tessellated into a Linked Halfedge by intersection computation.
  \item Coincident vertices between different Linked Halfedge should be linked, that is, coincident vertices are shared among Linked Halfedges.
  \item If a certain edge of Linked Halfedge is coincident with intersection line segment(s), it should be associated with the corresponding intersection context(s).
\end{itemize}

\subsection{Method Overview}

As illustrated in Fig. \ref{fig:overview}, we divide our methods into four steps as follows.

@@

This step is the preparation of intersection detection. As intersection detection is performed between each pair of faces, localization is necessary to filter invalid pairs beforehand. In general, any space division data structure can be applied in this step. We use the adaptive octree for its simplicity. Our implementation is akin to the implementation in \cite{ogayar2015deferred}. Intersection between triangle faces and octree leaves can be efficiently detected using the separating axis theorem \cite{gottschalk1996obbtree}. Octree leaves are classified into two types: if all faces that intersect a leaf belong to the same primitive, we call it a \emph{normal cell}. Otherwise, it is a \emph{critical cell}, within which the following intersection detection is performed.

The difference between our space division and Ogayar et al.'s is that we do not subdivide any normal cell no matter how many faces it contains. This is because subdividing normal cells benefits only the ray-casting point-in-polyhedron test  \cite{frisken2002simple}, which seldom uses in our method. This simplification can bring large performance advantage, especially for those cases where intersections between primitives are not complex and limited in small regions (e.g. Fig. \ref{fig:models}(x)).

@@

This step is to detect intersections between primitives in a robust and exact way. Our algorithm is largely based on vertex-based M\"{o}ller's algorithm \cite{moller1997fast}, which is very efficient to compute intersection between two triangles. However, naive implementation of M\"{o}ller's algorithm always incurs robustness issues. To avoid an unexpected failure caused by numeric errors, we integrate plane-based representation of polyhedra into M\"{o}ller's algorithm. All intersection vertices are represented using plane intersections to avoid geometry constructions. Also, we carefully identify all degenerate cases of triangle intersections, including point intersection, line intersection and coplanar intersection, and respectively discuss how to deal with each of them. Details are provided in Section \ref{section:isect}.

@@

Once all intersections are detected, we need to tessellate the input primitives and construct the Linked Halfedges. In many methods like \cite{ogayar2015deferred}, constraint Delaunay triangulation (CDT) is applied to perform tessellation, since the intersections are naturally the constraints of CDT. However, for a CSG with more than two primitives, the intersection vertices may be generated by intersections of three faces from different primitives, which cannot be computed during by triangle-triangle intersections in the previous step. Intersection line segments may overlap or intersect with each other, and cannot be used for constraints of CDT directly. In addition, as our intersection vertices are represented exactly by planes, implementation of CDT are complex and inefficient, as most CDT methods were not designed to handle planes and requires explicit coordinates. Therefore, we design a structure suited for plane-based representation, called \emph{Tess-graph}, to guide the tessellation of each single face, and develop a very fast but exact method to construct Linked Halfedges from Tess-graphs. Details are shown in section \ref{sec:tessellation}.

@@

This step is to choose faces from the Linked Halfedges to generate the final mesh. Literally computing all the space indicators of each face is unacceptably slow for large CSG trees. We utilize the geometry connectivity to accelerate this process. This is based on the observation that indicators of faces are locally coherent. Many method uses barycenters of faces together with point-in-polyhedra test for face classification, which is not exact nor robust with fix-precision float-point coordinates. Douze et al. \cite{douze2015quickcsg} classifies faces using space indicators of vertices, but failed to deal with coplanar conditions because of coplanar leads to ambiguity in such configurations. Different from all above, we classify faces based on the classification results of exactly represented vertices, including input vertices and newly introduced intersection vertices, and carefully deal with coplanar conditions to ensure topology consistency. Details will be shown in section \ref{sec:classification}.

@@

\begin{figure}
  \centering
  % Requires \usepackage{graphicx}
  \includegraphics[width=1.7in]{p-reps}\\
  \caption{Plane-based representation of triangles. The yellow triangle is represented by three bounding planes (green) and the supporting plane where the triangle lies.}\label{fig:p-reps}
\end{figure}
